---
title: "Summary report for the `r params$species`"
author: "Larissa Neilson"
output: html_document
params:
  species: species
---

### Your job: create a parameterized report using data from `penguins.csv`. 

- Your report should contain a ggplot graph of flipper length versus body mass for the **species** that you choose.

- Create a function that will render the report for the species you pick, saved as an .html with format 'penguin_report_SPECIESNAME.html'. 

- Create a function that will automatically render a separate report for *all species* in the data. 

```{r, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

```{r}
penguins <- read_csv("penguins.csv")

species_data <- penguins %>% 
  filter(species == params$species)

ggplot(data = species_data, aes(x = body_mass_g, y = flipper_length_mm)) +
  geom_point()
```

```{r, eval = FALSE}
render_penguins_report = function(species) {
  rmarkdown::render(
    input = "your_turn.Rmd", # What's the input file to render?
    params = list(species = species), # What are the parameters?
    output_file = paste0(species, "_report", ".html") # What should I name the output file?
  )
}

species_name <- unique(penguins$species)

for (species in species_name) {
    render_penguins_report(species)
}
```






